---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TCGAdecomp

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/TCGAdecomp)](https://CRAN.R-project.org/package=TCGAdecomp)
[![Codecov test coverage](https://codecov.io/gh/selkamand/TCGAdecomp/branch/master/graph/badge.svg)](https://app.codecov.io/gh/selkamand/TCGAdecomp?branch=master)
[![R-CMD-check](https://github.com/selkamand/TCGAdecomp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/selkamand/TCGAdecomp/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

TCGAdecomp is a data package containing each TCGA WGS dataset decomposed for SBS mutational signature analysis.

Original source of data is the TCGAmutations package, with catalogue powered by sigminer.


## Installation

You can install the development version of TCGAdecomp like so:

``` r
# install.packages('remotes')
remotes::install_github('selkamand/TCGAdecomp')
```

## Quick Start

List available datasets with `decomp_available()`

Load datasets with `decomp_load('dataset')`

```{r example}
library(TCGAdecomp)
# List available datasets
decomp_available()

# Load datasets
decomp_collection_acc <- decomp_load('ACC')

# Load datasets as data.frames
decomp_dataframe_acc <- decomp_load('ACC', dataframe = TRUE)
```

## Citation

If you find TCGAdecomp useful, please cite both *TCGAmutations*, *sigminer*, and the relevant TCGA study (which you can find by running `maftools::tcgaAvailable()`)
