---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TCGAcatalogues

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/TCGAcatalogues)](https://CRAN.R-project.org/package=TCGAcatalogues)
[![Codecov test coverage](https://codecov.io/gh/selkamand/TCGAcatalogues/branch/master/graph/badge.svg)](https://app.codecov.io/gh/selkamand/TCGAcatalogues?branch=master)
[![R-CMD-check](https://github.com/selkamand/TCGAcatalogues/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/selkamand/TCGAcatalogues/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

TCGAcatalogues makes it simple to load mutation catalogues of TCGA cohorts for downstream applications including mutational signature analysis.

Original source of data is the [TCGAmutations](https://github.com/PoisonAlien/TCGAmutations) package, with catalogues generated by [sigminer](https://github.com/ShixiangWang/sigminer).


## Installation

You can install the development version of TCGAcatalogues like so:

``` r
if (!require("pak", quietly = TRUE))
    install.packages("pak")

pak::pak("selkamand/TCGAcatalogues")
```

## Quick Start

List available datasets with `catalogues_available()`

Load datasets with `catalogues_load('dataset')`

```{r example}
library(TCGAcatalogues)
# List available datasets
catalogues_available()

# Load datasets
catalogues_collection_acc <- catalogues_load('ACC')

# Load datasets as data.frames
catalogues_dataframe_acc <- catalogues_load('ACC', dataframe = TRUE)
```

## Citation

If you find TCGAcatalogues useful, please cite both *TCGAmutations*, *sigminer*, and the relevant TCGA study (which you can find by running `maftools::tcgaAvailable()`)
